Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
On with Results

\subsection{Results}
\label{sec:results}

>>>>

\subsection{Results}
\label{sec:results}
At the end of the experiment the resulting log file contained 933,513 contributions both 
registered users and anonymous volunteers. Registered users where responsible of around
90\% of the contributions. The JSON data recorded for each contribution is  presented 
in Table~\ref{tab:record}.  
\begin{table}
  \small
  \caption{ Logfile record structure}
  \label{tab:record} 
  \centering
  \small
  \begin{tabular}{l  l}
    \hline\noalign{\smallskip}
     Attribute & Value \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
    fitness & fitness as an integer.  \\ \hline
    IP & IP address of the participant (later anonymized) .\\ \hline
    user & user-name or the string `anonymous'.  \\ \hline
    worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
    level &  level of user or the string `info' \\ \hline
    message & Only PUT messages were recorded in this experiment. \\ \hline
    timestamp & A time-stamp based on the Unix epoch\\ \hline
  \end{tabular}
\end{table}
